Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-10 minimax.tex
Less redundancies

Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative. Finally, we find out experimentally that questioning agents is more useful than questioning the chair in our setting.
\end{abstract}

@@

The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand. These represent two strong hypothesis.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015,Benabbou2016} of agent preferences. \\ 
Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method. Thus, the first hypothesis should also be relaxed. 
%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.

@@

The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.

@@

\Citet{Konczak05} were the first to consider the problem of computing, for various voting rules, possible and necessary winners in the case of partial knowledge of agent preferences and showed that the problem is hard in the general case.
This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.

@@

More recently \citet{Llamazares2013} and \citet{Viappiani2018} %(among others \commentOC{Which others?}) 
considered the problem of dealing with unspecified weights in positional scoring rules; the first proposed a method based on Data Envelopment Analysis (DEA), while the second proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret). 
The work of \citet{Cailloux2014} deals with the problem of eliciting a generic voting rule.

Finally we also mention works related to the manipulability of voting rules %have been proposed in this context 
\citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and work concerning strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%$150$ questions?
%Pessimistic systematically better than XPess?
%\end{enumerate}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
a sequence of convex decreasing weight is then obtained by a decumulative sum.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

>>>>

Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative. Finally, we study these strategies experimentally in order to validate our approach and obtain practical guidelines.
\end{abstract}

@@

The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand. These represent two strong hypothesis.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated a number of recent works considering social choice with partial preference orders and incremental elicitation of agent preferences. 
Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method. Thus, the first hypothesis should also be relaxed. 
%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.

@@

The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
\Cref{sec:background} provides the necessary background and \cref{sec:mmr} introduces the minimax criterion, a method that selects a winner that minimizes the worst possible regret.
In Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  Section \ref{sec:experiments} presents the experiments validation of our approach and the guidelines stemming from these simulations; and Section \ref{sec:conclusions} provides some final thoughts.

@@

\Citet{Konczak05} studied the computation of possible and necessary winners in the case of partial knowledge of agent preferences, for various voting rules, and showed that the problem is hard in the general case.
This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin.
In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.

@@

More recent articles considered the problem of dealing with unspecified weights in positional scoring rules: \citet{Llamazares2013} proposed a method based on Data Envelopment Analysis (DEA), while \citet{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret). 
\Citet{Cailloux2014} are interested in elicitation of a different class of rules.

Finally, we mention works related to the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011}, and studies of strategic behaviors, when agents learn incrementally about other agent preferences \citep{Endriss2016,Lev2019,Annemieke2012}.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%$150$ questions?
%Pessimistic systematically better than XPess?
%Page numbers
%reflexive?
%\end{enumerate}
We  performed a number of numerical experiments in order to validate our approach and to test the performance of the different elicitation strategies. %Our experiments are described by topic here below. 
We start by describing the general protocol of experimentation. %use the following protocol, deviations are indicated below for each experiment.
Having picked a problem size $(m, n)$, a number of questions $k$ and a strategy to test, we randomly generate an “oracle”, containing the true preferences of the agents (i.e. the linear orders) and the weights associated with the chair's scoring rule. 
The preferences are generated following an impartial culture assumption: the linear order of each agent is generated independently from the other ones and all have the same probability of appearing. 
For generating the weights we first draw $m - 1$ numbers uniformly at random (representing weight ``differences''), normalize and sort them; 
a sequence of convex decreasing weight is then obtained by a decumulative sum.
The penalty parameters for the Pessimistic and Extended pessimistic strategies are set to $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
